Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-06-26 R0V0.tex
Update the statement of Proposition 1

\begin{theorem}\label{thm:main result}
	If there exists a solution to the matrix inequalities
	\begin{subequations}\label{eq:main result}
		\begin{equation}\label{eq:MI:SSCCM}
			-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0
		\end{equation}
		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
		\begin{equation}\label{eq:Ws:SSCCM}
			W_i\succ0, W_i\in\Pi_i,\forall i\in\mathbb{N}_{[1,N]}
		\end{equation}
		and
		\begin{equation}\label{eq:YinXi}
			Y\in\Xi.
		\end{equation}
	\end{subequations}
	Then, $W$ is a separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

@@

\begin{corollary}[{\cite{SteinShiromotoManchester2016}}]\label{cor:main result}
	Assume that the matrix $B$ satisfies the identity
	\begin{equation*}
		\partial_BW-\tfrac{\partial B}{\partial x}W-W\tfrac{\partial B}{\partial x}^\top\equiv0
	\end{equation*}
	and there exist $N$ functions $\rho_i:\mathbb{R}^{n_i+\vec{n}_i}\to\mathbb{R}$ such that the matrix inequality
	\begin{equation}\label{eq:with R}
		-\dot{W}+\tfrac{\partial f}{\partial x}W+W\tfrac{\partial f}{\partial x}^\top-BRB^\top-2\lambda W\prec0
	\end{equation}
	holds uniformly with respect to $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, where $R=\mathbin{\mathtt{diag}}(\rho_1,\ldots,\rho_N)$. Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the functions $\rho_i$.
\end{corollary}

@@

\begin{proposition}\label{prop:clique tree decomposition}
	Let $\mathscr{G}:=\mathscr{G}_p\cup\mathscr{G}_c$ and $l\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$. Then, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $p$ matrix inequalities with smaller dimension. Moreover, if each matrix is negative definite, then the MI~\eqref{eq:MI:SSCCM} is satisfied.
\end{proposition}

>>>>

\begin{theorem}\label{thm:main result}
	If there exists a solution to the matrix inequalities
	\begin{subequations}\label{eq:main result}
		\begin{equation}\label{eq:MI:SSCCM}
			-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0
		\end{equation}
		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
		\begin{equation}\label{eq:Ws:SSCCM}
			W_i\succ0, W_i\in\Pi_i,\forall i\in\mathbb{N}_{[1,N]}
		\end{equation}
		and
		\begin{equation}\label{eq:YinXi}
			Y\in\Xi.
		\end{equation}
	\end{subequations}
	Then, $W$ is a separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, each function $W_i$ depends only on the state of system $i$. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

@@

\begin{corollary}[{\cite{SteinShiromotoManchester2016}}]\label{cor:main result}
	Assume that the matrix $B$ satisfies the identity
	\begin{equation*}
		\partial_BW-\tfrac{\partial B}{\partial x}W-W\tfrac{\partial B}{\partial x}^\top\equiv0
	\end{equation*}
	and there exist $N$ functions $\rho_i:\mathbb{R}^{n_i+\vec{n}_i}\to\mathbb{R}$ such that the matrix inequality
	\begin{equation}\label{eq:with R}
		-\dot{W}+\tfrac{\partial f}{\partial x}W+W\tfrac{\partial f}{\partial x}^\top-BRB^\top-2\lambda W\prec0
	\end{equation}
	holds uniformly with respect to $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, where $R=\mathbin{\mathtt{diag}}(\rho_1,\ldots,\rho_N)$. Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. Also, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the functions $\rho_i$.
\end{corollary}

@@

\begin{proposition}\label{prop:clique tree decomposition}
	Let $\mathscr{G}:=\mathscr{G}_p\cup\mathscr{G}_c$ and $l\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$. Then, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $l$ matrix inequalities with smaller dimension. Furthermore, each of the matrix inequality correspond to a clique, and for each node $i\in\mathscr{V}_p\cup\mathscr{V}_c$ contained in it, the matrix inequality depends on $x_i, \breve{x}_i$ and $\vec{x}_i$. Finally, whenever each matrix inequality holds uniformly over its argument, the set of Equations~\eqref{eq:MI:SSCCM} is satisfied.
\end{proposition}
